Compositional equivalences based on Open pNets

### 2020-02-04 2016-Weak-FH-Bisim/WeakBisim.tex

\TODO{Eric: insert here a table with the details of the WOTs...}

@@

\smallskip
$2^nd$ try, full formal style ?:

$$ 1 = \openrule
         {\{P\mapsto\texttt{p-a}\}, [\forall m.p-a!=P\_send(m)], () }
         {000 \OTWeakarrow {\texttt{p-a}} 000}$$
\\
$$6 = \openrule
         {\{\}, [True], () }
         {100 \OTWeakarrow {\tau\big(\subst{m1\_c:=s1\_c,m1\_m:=s1\_m,s2\_c:=s1\_c}\subst{s1\_c:=s2\_c+1}\big)^* \subst{m1\_c:=s1\_c,m1\_m:=s1\_m,s2\_c:=s1\_c} } 210}
         $$

>>>>

\TODO{Eric: insert here a table with the details of the WOTs.Il manque encore au moins 3 WOT dans ce dessin...}

@@

\smallskip
$2^nd$ try, full formal style ?:
\medskip

Here we denote as $post_n$ the effect of the Strong transition $OT_n$ from Figure \ref{}:
\smallskip

$post_1 = post_2 = ()$

$post_3 = (s1\_c\gets 0, s1\_m\gets m)$

$post_4 = (m1\_msg\gets s1\_msg, m1\_c\gets s1\_c)$

$post_5 = (m2\_c\gets m1\_c)$

$post_6 = (s1\_c\gets m2\_c+1)$

$post_7 = (r1\_msg\gets m1\_msg, r1\_c\gets m1\_c)$

$post_8 = ()$
\medskip

Then the effect of one single $100 -> 210 -> 220 -> 100$ loop as:
\smallskip

$Post_{456} = post_6\shortotimes post_5\shortotimes post_4$
\medskip

And we can now define the weak OTs:
\smallskip

$ 1 = \openrule
{\{P\mapsto p\_a\}, [\forall m. p\_a \neq p\_send(m)], ()}
{000 \OTWeakarrow {\tau} 000}
$

$ 3 = \openrule
         {\{P\mapsto p\_send(m)\}, True, post_4\shortotimes {Post_{456}}^*\shortotimes\ post_3}
         {000 \OTWeakarrow {\texttt{in(m)}} 100}$

$ 4 = \openrule
         {\{\}, True, post_4\shortotimes {Post_{456}}^* }
         {100 \OTWeakarrow {\tau} 210}
         $

$ 5 = \openrule
         {\{\}, True, {Post_{564}}^* }
         {210 \OTWeakarrow {\tau} 220}
         $

$ 6 = \openrule
         {\{\}, True, {Post_{456}}^*\shortotimes post_6 }
         {220 \OTWeakarrow {\tau} 100}
         $

$ 7 = \openrule
         {\{\}, True, post_7\shortotimes {Post_{564}}^* }
         {220 \OTWeakarrow {\tau} 100}
         $
